Measuring Software Ticket Quality using Statistical Analysis

### 2017-12-13 proposal/mprop.tex
Wrap up first subsection of the introduction

@@

Having discussed about the high level of abstraction computers expose to 
their human operators, developing software that runs and performs as expected
in agreement with its requirements is not trivial. Thus, developers have
created software called \emph{issue tracking systems} that can manage
and track \emph{tickets}, which can take various forms, such as bug 
reports, feature requests etc. The aforementioned tickets can vary greatly
and issue tracking systems usually allow developers to include many 
types of information, such as:
  \begin{itemize}
    \item stack traces;
    \item steps to reproduce a bug;
    \item summary and description;
    \item story points (e.g. how many units of time does it take one
      developer to mark the ticket as resolved or completed).
  \end{itemize}

Thus, a still unresolved software engineering issue is how can one create
valuable, high quality tickets?

>>>>

\subsection{Background}

@@

Having discussed about the high level of abstraction computers expose to 
their human operators, developing software that runs and performs as expected
in agreement with its requirements is not trivial. Thus, developers have
created software called \emph{issue tracking systems} that can manage
and track \emph{tickets}, which can take various forms, such as bug 
reports, feature requests etc. The aforementioned tickets can vary greatly
and issue tracking systems usually allow developers to include many 
types of information, such as:
  \begin{itemize}
    \item stack traces;
    \item steps to reproduce a bug;
    \item summary and description;
    \item story points (e.g. how many units of time does it take one
      developer to mark the ticket as resolved or completed).
  \end{itemize}
In order to create such tickets, the end users or the developers 
themselves notice certain flaws in the software or propose new features
to be implemented. Then, they head to the issue tracking system and 
create tickets where they provide information wrapped up in a ticket.
However, we are facing a main issue here, and that is what do developers 
on the project find most important when fixing a bug/implementing a 
new feature.

Therefore, a software engineering issue still not completely resolved
is how can one create valuable, high quality tickets?

\subsection{Problem Statement}

This research is trying to investigate the various components of a 
issue tracking system ticket and specific characteristics

\subsection{Research Questions and Contributions}

\subsection{Proposal Structure}
